DeepTriangle: A Deep Learning Approach to Loss Reserving

### 2019-08-07 manuscript/manuscript.Rmd

```{r, echo = FALSE, results="asis", message = FALSE}
predictions <- feather::read_feather("data/predictions.feather")
automl_results <- read_csv("data/automl_results.csv")
model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(automl_results) %>%
  gather(metric, value, mape, rmspe)
mape_table <- dt_tabulate_metrics(model_results, "mape")
rmspe_table <- dt_tabulate_metrics(model_results, "rmspe")
bind_rows(mape_table, rmspe_table) %>%
  mutate(lob = case_when(
    lob == "commercial_auto" ~ "Commercial Auto",
    lob == "other_liability" ~ "Other Liability",
    lob == "private_passenger_auto" ~ "Private Passenger Auto",
    lob == "workers_compensation" ~ "Workers' Compensation"
  )) %>%
  rename(DT = DeepTriangle,
         ML = AutoML,
         `Line of Business` = lob) %>%
  knitr::kable(
    format = "latex", booktabs = "T",
    digits = 3,
    caption = "\\label{tab:table1}Performance comparison of various models. DeepTriangle and AutoML are abbreviated do DT and ML, respectively."
  ) %>%
  kableExtra::column_spec(7, bold = TRUE) %>%
  kableExtra::group_rows("MAPE", 1, 4) %>%
  kableExtra::group_rows("RMSPE", 5, 8)
```

>>>>

```{r, echo = FALSE, results="asis", message = FALSE}
data_dir <- file.path(here::here(), "datasets")
predictions <- feather::read_feather(file.path(data_dir, "predictions.feather"))
automl_results <- read_csv(file.path(data_dir, "automl_results.csv"))
model_results <- dt_compute_metrics(predictions) %>%
  bind_rows(stochastic_model_results) %>%
  bind_rows(automl_results) %>%
  gather(metric, value, mape, rmspe)
mape_table <- dt_tabulate_metrics(model_results, "mape")
rmspe_table <- dt_tabulate_metrics(model_results, "rmspe")
bind_rows(mape_table, rmspe_table) %>%
  mutate(lob = case_when(
    lob == "commercial_auto" ~ "Commercial Auto",
    lob == "other_liability" ~ "Other Liability",
    lob == "private_passenger_auto" ~ "Private Passenger Auto",
    lob == "workers_compensation" ~ "Workers' Compensation"
  )) %>%
  rename(DT = DeepTriangle,
         ML = AutoML,
         `Line of Business` = lob) %>%
  knitr::kable(
    format = "latex", booktabs = "T",
    digits = 3,
    caption = "\\label{tab:table1}Performance comparison of various models. DeepTriangle and AutoML are abbreviated do DT and ML, respectively."
  ) %>%
  kableExtra::column_spec(7, bold = TRUE) %>%
  kableExtra::group_rows("MAPE", 1, 4) %>%
  kableExtra::group_rows("RMSPE", 5, 8)
```
